Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-11 overview.tex
Added sentence clarifying B definition.

\begin{eqnarray}
\vecx & = & \vecx' / a, \\
\vecv & = & a \hspace{0.5mm} \dot{\vecx} = 
              \vecvp - \dot{a}\vecx, \\
\rho  & = & a^3 \rhop,   \\
p     & = & a^3 \pp, \\
E     & = & a^3 \left(\Ep - 
            \dot{a} \, \vecx \cdot \vecvp - 
            \frac{1}{2} \dot{a}^2 \vecx^2\right), \\
\phi  & = & \phip + \frac{1}{2} \, a \ddot{a} \, \vecx^2, \\
\vecB & = & a^2 \vecB^\prime,
\end{eqnarray}
where primes indicate quantities in proper coordinates (fixed frame).
%These definitions result in the following comoving equivalents to eqs. 
%(\ref{eq:mass})-(\ref{eq:potential}).
%%
%
%\begin{eqnarray} 
%\frac{\partial \rhop}{\partial t} 
%          + \frac{1}{a} \vecvp \cdot \grad \rhop 
%    & = & - \frac{1}{a} \rhop \div \vecvp, 
%        \label{eq:mass_prime} \\
%%
%\frac{\partial \vecvp}{\partial t}  
%          + \frac{1}{a} ( \vecvp \cdot \grad ) \vecvp 
%    & = & - \frac{\dot{a}}{a} \vecvp 
%          - \frac{1}{a \rhop} \grad \pp 
%          - \frac{1}{a} \grad \phip, 
%        \label{eq:momentum_prime} \\
%%
%\frac{\partial \Ep}{\partial t} 
%         + \frac{1}{a} \vecvp \cdot \grad \Ep 
%   & = & - \frac{\dot{a}}{a} (3 \frac{\pp}{\rhop} + {\vecvp \cdot \vecvp} )
%         - \frac{1}{a \rhop } \div (p \vecvp) 
%%\nonumber   & &   %uncomment for 2-column
%         - \frac{1}{a} \vecvp \cdot \grad \phip 
%                + \Gamma - \Lambda.
%       \label{eq:total_energy_prime} \\
%%
%\Ep  & = & \ep + \frac{1}{2} {\vecvp \cdot \vecvp},
%        \label{eq:total_energy_def_prime} \\
%%
%\ep                  & = & 
%        \pp/\left[ \left( \gamma - 1 \right) \rhop \right],
%      \label{eq:state_prime} \\ 
%{\nabla}^2 \phip    & = & 
%        \frac{4\pi G}{a} ( \rhop_{total} - \rhop_0 ).
%      \label{eq:poisson}
%\end{eqnarray}
%%
%%We use the proper peculiar baryonic velocity $\vecv_b \equiv a(t) d\vecx / dt$, proper pressure $p$, and modified gravitational potential $ \phi $ which is related to the potential in proper coordinates $\Phi$ by 
%%$$\phi \equiv \Phi + \frac{1}{2} a \ddot{a} \vecx^2. $$
%%The density, however, is comoving:
%%$$\rho_b \equiv \rho_{b,proper}a(t)^3, $$
The expansion parameter $a \equiv 1/(1 + z)$ follows the expansion of
a smooth, homogeneous background, where $z$, the redshift, is a
function only of $t$.  All spatial derivatives are determined with
respect to the comoving position $\vecx$, which removes the universal
expansion from the coordinate system. The evolution of $a(t)$ is
governed by the second Friedmann equation for the expansion of a
spatially homogeneous and isotropic universe
%
\begin{eqnarray}
\frac{\ddot{a}}{a} & = & 
      - \frac{4 \pi G }{3 a^3 } (\rho_0 
      + 3p_0/c^2) 
      + \Lambda_c c^2 / 3 .
      \label{eq:expansion} 
\end{eqnarray}
%
Here $\rho_0$ is the mean comoving mass density (including both
baryonic and dark matter), $p_0$ is the comoving background pressure
contribution, and $\Lambda_c$ is the cosmological constant.
%$\gamma$ is the ratio of specific heats, and $\Lambda$ is the cosmological constant.
%We note that if $\gamma$ is not $5/3$ then $E$ in the first term on
%the right side of eq.~(ref{eq:total_energy}) must be replaced with 
%eq.~(\ref{eq:state}).
This system of equations is limited to the non-relativistic regime and
assumes that curvature effects are not important --- both assumptions
are reasonable as long as the size of the simulated region is small
compared to the radius of curvature and the Hubble length $c/H$, where
$c$ is the speed of light and $H = \dot{a}/a$ is the Hubble constant.

>>>>

\begin{eqnarray}
\vecx & = & \vecx' / a, \\
\vecv & = & a \hspace{0.5mm} \dot{\vecx} = 
              \vecvp - \dot{a}\vecx, \\
\rho  & = & a^3 \rhop,   \\
p     & = & a^3 \pp, \\
E     & = & a^3 \left(\Ep - 
            \dot{a} \, \vecx \cdot \vecvp - 
            \frac{1}{2} \dot{a}^2 \vecx^2\right), \\
\phi  & = & \phip + \frac{1}{2} \, a \ddot{a} \, \vecx^2, \\
\vecB & = & a^2 \vecB^\prime,
\end{eqnarray}
where primes indicate quantities in proper coordinates (fixed frame).
We note that the definition of comoving $\vecB$ used here is such
that a uniform field is constant in a homogeneous, uniform universe
and is also the quantity used in the MHD-Dedner solver described
below; however, it is not universal,
and in particular is slightly different from that used both in \citet{Li08a}
and that used in the MHD-CT solver.
%These definitions result in the following comoving equivalents to eqs. 
%(\ref{eq:mass})-(\ref{eq:potential}).
%%
%
%\begin{eqnarray} 
%\frac{\partial \rhop}{\partial t} 
%          + \frac{1}{a} \vecvp \cdot \grad \rhop 
%    & = & - \frac{1}{a} \rhop \div \vecvp, 
%        \label{eq:mass_prime} \\
%%
%\frac{\partial \vecvp}{\partial t}  
%          + \frac{1}{a} ( \vecvp \cdot \grad ) \vecvp 
%    & = & - \frac{\dot{a}}{a} \vecvp 
%          - \frac{1}{a \rhop} \grad \pp 
%          - \frac{1}{a} \grad \phip, 
%        \label{eq:momentum_prime} \\
%%
%\frac{\partial \Ep}{\partial t} 
%         + \frac{1}{a} \vecvp \cdot \grad \Ep 
%   & = & - \frac{\dot{a}}{a} (3 \frac{\pp}{\rhop} + {\vecvp \cdot \vecvp} )
%         - \frac{1}{a \rhop } \div (p \vecvp) 
%%\nonumber   & &   %uncomment for 2-column
%         - \frac{1}{a} \vecvp \cdot \grad \phip 
%                + \Gamma - \Lambda.
%       \label{eq:total_energy_prime} \\
%%
%\Ep  & = & \ep + \frac{1}{2} {\vecvp \cdot \vecvp},
%        \label{eq:total_energy_def_prime} \\
%%
%\ep                  & = & 
%        \pp/\left[ \left( \gamma - 1 \right) \rhop \right],
%      \label{eq:state_prime} \\ 
%{\nabla}^2 \phip    & = & 
%        \frac{4\pi G}{a} ( \rhop_{total} - \rhop_0 ).
%      \label{eq:poisson}
%\end{eqnarray}
%%
%%We use the proper peculiar baryonic velocity $\vecv_b \equiv a(t) d\vecx / dt$, proper pressure $p$, and modified gravitational potential $ \phi $ which is related to the potential in proper coordinates $\Phi$ by 
%%$$\phi \equiv \Phi + \frac{1}{2} a \ddot{a} \vecx^2. $$
%%The density, however, is comoving:
%%$$\rho_b \equiv \rho_{b,proper}a(t)^3, $$
The expansion parameter $a \equiv 1/(1 + z)$ follows the expansion of
a smooth, homogeneous background, where $z$, the redshift, is a
function only of $t$.  All spatial derivatives are determined with
respect to the comoving position $\vecx$, which removes the universal
expansion from the coordinate system. The evolution of $a(t)$ is
governed by the second Friedmann equation for the expansion of a
spatially homogeneous and isotropic universe
%
\begin{eqnarray}
\frac{\ddot{a}}{a} & = & 
      - \frac{4 \pi G }{3 a^3 } (\rho_0 
      + 3p_0/c^2) 
      + \Lambda_c c^2 / 3 .
      \label{eq:expansion} 
\end{eqnarray}
%
Here $\rho_0$ is the mean comoving mass density (including both
baryonic and dark matter), $p_0$ is the comoving background pressure
contribution, and $\Lambda_c$ is the cosmological constant.
%$\gamma$ is the ratio of specific heats, and $\Lambda$ is the cosmological constant.
%We note that if $\gamma$ is not $5/3$ then $E$ in the first term on
%the right side of eq.~(ref{eq:total_energy}) must be replaced with 
%eq.~(\ref{eq:state}).
This system of equations is limited to the non-relativistic regime and
assumes that curvature effects are not important --- both assumptions
are reasonable as long as the size of the simulated region is small
compared to the radius of curvature and the Hubble length $c/H$, where
$c$ is the speed of light and $H = \dot{a}/a$ is the Hubble constant.
